---
title: "End-Semester Course Evaluation Results"
# author: "Allan Omondi"
# date: "`r Sys.Date()`"
output:
  html_document: 
    toc: yes
    df_print: kable
    fig_width: 8
    fig_height: 8
    fig_caption: yes
    toc_depth: 4
    keep_md: yes
    css: CSS_Chunk.css
  html_notebook: default
  pdf_document:
    toc: yes
    number_sections: yes
    fig_width: 8
    fig_height: 8
    fig_caption: yes
    keep_tex: yes
  always_allow_html: true
  word_document:
    toc: yes
---

+-----------------------------------------------------------------------------------------+-------------------------------------------------------------------------+
| **Course**                                                                              | Business Intelligence II                                                |
+-----------------------------------------------------------------------------------------+-------------------------------------------------------------------------+
| **Course Code**                                                                         | BBT4206                                                                 |
+-----------------------------------------------------------------------------------------+-------------------------------------------------------------------------+
| **Class**                                                                               | BBIT 4.2                                                                |
+-----------------------------------------------------------------------------------------+-------------------------------------------------------------------------+
| **Semester Duration**                                                                   | 21^st^ August 2023 to 28^th^ November 2023                              |
+-----------------------------------------------------------------------------------------+-------------------------------------------------------------------------+
| **Date of Evaluation**                                                                  | 21^st^ November 2023 to 27^th^ November 2023 (Week 14 of 14)            |
+-----------------------------------------------------------------------------------------+-------------------------------------------------------------------------+
| **Total number of students who submitted the course evaluation**                        | 107                                                                     |
+-----------------------------------------------------------------------------------------+-------------------------------------------------------------------------+
| **Total number of students registered in the AMS at the time of the course evaluation** | 114                                                                     |
+-----------------------------------------------------------------------------------------+-------------------------------------------------------------------------+
| **Response rate**                                                                       | 94%                                                                     |
+-----------------------------------------------------------------------------------------+-------------------------------------------------------------------------+
| **e-Learning URL**                                                                      | <https://elearning.strathmore.edu/course/view.php?id=6599>              |
+-----------------------------------------------------------------------------------------+-------------------------------------------------------------------------+
| **Data collection tool URL\                                                             | <https://elearning.strathmore.edu/mod/questionnaire/view.php?id=221959> |
| (for access to the raw data)**                                                          |                                                                         |
+-----------------------------------------------------------------------------------------+-------------------------------------------------------------------------+
| **Lecturer**                                                                            | Dr Allan Omondi \<aomondi\@strathmore.edu\>                             |
+-----------------------------------------------------------------------------------------+-------------------------------------------------------------------------+

------------------------------------------------------------------------

```{r InstallandLoadtheRequiredPackages, include=FALSE, warning=FALSE}
# Install and Load the Required Packages ----
# The following packages can be installed and loaded before proceeding to 
# the subsequent steps.

## dplyr - For data manipulation ----
if (!is.element("dplyr", installed.packages()[, 1])) {
  install.packages("dplyr", dependencies = TRUE)
}
require("dplyr")

## ggplot2 - For data visualizations using the Grammar for Graphics package ----
if (!is.element("ggplot2", installed.packages()[, 1])) {
  install.packages("ggplot2", dependencies = TRUE)
}
require("ggplot2")

## ggrepel - Additional options for the Grammar for Graphics package ----
if (!is.element("ggrepel", installed.packages()[, 1])) {
  install.packages("ggrepel", dependencies = TRUE)
}
require("ggrepel")

## ggraph - Additional options for the Grammar for Graphics package ----
if (!is.element("ggraph", installed.packages()[, 1])) {
  install.packages("ggraph", dependencies = TRUE)
}
require("ggraph")

## tidytext - For text mining ----
if (!is.element("tidytext", installed.packages()[, 1])) {
  install.packages("tidytext", dependencies = TRUE)
}
require("tidytext")

## tidyr - To tidy messy data ----
if (!is.element("tidyr", installed.packages()[, 1])) {
  install.packages("tidyr", dependencies = TRUE)
}
require("tidyr")

## widyr - To widen, process, and re-tidy a dataset ----
if (!is.element("widyr", installed.packages()[, 1])) {
  install.packages("widyr", dependencies = TRUE)
}
require("widyr")

## gridExtra - to arrange multiple grid-based plots on a page ----
if (!is.element("gridExtra", installed.packages()[, 1])) {
  install.packages("gridExtra", dependencies = TRUE)
}
require("gridExtra")

## knitr - for dynamic report generation ----
if (!is.element("knitr", installed.packages()[, 1])) {
  install.packages("knitr", dependencies = TRUE)
}
require("knitr")

## devtools ----
if (!is.element("devtools", installed.packages()[, 1])) {
  install.packages("devtools", dependencies = TRUE)
}
require("devtools")

## kableExtra - for nicely formatted output tables ----
#if (!is.element("kableExtra", installed.packages()[, 1])) {
#  install.packages("kableExtra", dependencies = TRUE)
#}
#require("kableExtra")
# The following kableExtra is used as an alternative to the one
# stored in CRAN because of the errors when rendering to PDF.
devtools::install_github("kupietz/kableExtra")
require("kableExtra")

## formattable -  To create a formattable object ----
# A formattable object is an object to which a formatting function and related
# attributes are attached.
if (!is.element("formattable", installed.packages()[, 1])) {
  install.packages("formattable", dependencies = TRUE)
}
require("formattable")

## circlize - To create a cord diagram or visualization ----
# by Gu et al. (2014)
if (!is.element("circlize", installed.packages()[, 1])) {
  install.packages("circlize", dependencies = TRUE)
}
require("circlize")

## memery - For creating data analysis related memes ----
# The memery package generates internet memes that optionally include a
# superimposed inset plot and other atypical features, combining the visual
# impact of an attention-grabbing meme with graphic results of data analysis.
if (!is.element("memery", installed.packages()[, 1])) {
  install.packages("memery", dependencies = TRUE)
}
require("memery")

## magick - For image processing in R ----
if (!is.element("magick", installed.packages()[, 1])) {
  install.packages("magick", dependencies = TRUE)
}
require("magick")

## yarrr - To create a pirate plot ----
if (!is.element("yarrr", installed.packages()[, 1])) {
  install.packages("yarrr", dependencies = TRUE)
}
require("yarrr")

## radarchart - To create interactive radar charts using ChartJS ----
if (!is.element("radarchart", installed.packages()[, 1])) {
  install.packages("radarchart", dependencies = TRUE)
}
require("radarchart")

## igraph - To create ngram network diagrams ----
if (!is.element("igraph", installed.packages()[, 1])) {
  install.packages("igraph", dependencies = TRUE)
}
require("igraph")

## wordcloud2 - For creating wordcloud by using 'wordcloud2.JS ----
if (!is.element("wordcloud2", installed.packages()[, 1])) {
  install.packages("wordcloud2", dependencies = TRUE)
}
require("wordcloud2")

## textdata - Download sentiment lexicons and labeled text data sets ----
if (!is.element("textdata", installed.packages()[, 1])) {
  install.packages("textdata", dependencies = TRUE)
}
require("textdata")

## readr - Load datasets from CSV files ----
if (!is.element("readr", installed.packages()[, 1])) {
  install.packages("readr", dependencies = TRUE)
}
require("readr")

## stringr - For processing characters in a string ----
if (!is.element("stringr", installed.packages()[, 1])) {
  install.packages("stringr", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
require("stringr")

## ggcorrplot - For correlation plots ----
if (!is.element("ggcorrplot", installed.packages()[, 1])) {
  install.packages("ggcorrplot", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
require("ggcorrplot")

## reshape2 - For formatting correlation plots ----
if (!is.element("reshape2", installed.packages()[, 1])) {
  install.packages("reshape2", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
require("reshape2")

## textstem - Used to lemmatize words ----
if (!is.element("textstem", installed.packages()[, 1])) {
  install.packages("textstem", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
require("textstem")

## hunspell - High-Performance Stemmer, Tokenizer, and Spell Checker ----
if (!is.element("hunspell", installed.packages()[, 1])) {
  install.packages("hunspell", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
require("hunspell")

## stringr - For processing characters in a string ----
if (!is.element("stringr", installed.packages()[, 1])) {
  install.packages("stringr", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
require("stringr")

## webshot2 - To ensure that HTML content is shown as a screenshot ----
if (!is.element("webshot2", installed.packages()[, 1])) {
  install.packages("webshot2", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
require("webshot2")

## caret - To create multivariate box and whisker plots ----
if (!is.element("caret", installed.packages()[, 1])) {
  install.packages("caret", dependencies = TRUE)
}
require("caret")

## tm - For text mining (qualitative data analysis) ----
if (!is.element("tm", installed.packages()[, 1])) {
  install.packages("tm", dependencies = TRUE)
}
require("tm")

## plotly - For interactive ggplot graphs ----
if (!is.element("plotly", installed.packages()[, 1])) {
  install.packages("plotly", dependencies = TRUE)
}
require("plotly")

## lda - For Latent Dirichlet Allocation (LDA) used for topic modelling ----
if (!is.element("lda", installed.packages()[, 1])) {
  install.packages("lda", dependencies = TRUE)
}
require("lda")

## topicmodels - For an interface to the C code for LDA models ----
if (!is.element("topicmodels", installed.packages()[, 1])) {
  install.packages("topicmodels", dependencies = TRUE)
}
require("topicmodels")
```

```{r CustomizetheVisualizations, include=FALSE, warning=FALSE}
# Customize the Visualizations, Tables, and Colour Scheme ----
# The following defines a blue-grey colour scheme for the visualizations:
## shades of blue and shades of grey
blue_grey_colours_11 <- c("#27408E", "#304FAF", "#536CB5", "#6981c7", "#8da0db",
                          "#dde5ec", "#c8c9ca", "#B9BCC2", "#A7AAAF", "#888A8E",
                          "#636569")

blue_grey_colours_6 <- c("#27408E", "#304FAF", "#536CB5",
                         "#B9BCC2", "#A7AAAF", "#888A8E")

blue_grey_colours_4 <- c("#27408E", "#536CB5",
                         "#B9BCC2", "#888A8E")

blue_grey_colours_3 <- c("#6981c7", "#304FAF", "#888A8E")

blue_grey_colours_2 <- c("#27408E",
                         "#888A8E")

blue_grey_colours_1 <- c("#6981c7")

# Custom theme for visualizations
blue_grey_theme <- function() {
  theme(
    axis.ticks = element_line(
                              linewidth = 1, linetype = "dashed",
                              lineend = NULL, color = "#dfdede",
                              arrow = NULL, inherit.blank = FALSE),
    axis.text = element_text(
                             face = "plain", color = "#3f3f41",
                             size = 12, hjust = 0.5),
    axis.title = element_text(face = "plain", color = "#3f3f41",
                              size = 12, hjust = 0.5),
    plot.title = element_text(face = "bold", color = "#3f3f41",
                              size = 12, hjust = 0.5),
    panel.grid = element_line(
                              linewidth = 0.1, linetype = "dashed",
                              lineend = NULL, color = "#dfdede",
                              arrow = NULL, inherit.blank = FALSE),
    panel.background = element_rect(fill = "#f3eeee"),
    legend.title = element_text(face = "plain", color = "#3f3f41",
                                size = 12, hjust = 0),
    legend.position = "right"
  )
}

# Customize the text tables for consistency using HTML formatting
my_kable_styling <- function(dat, caption) {
  knitr::kable(dat, "html", escape = FALSE, caption = caption) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "condensed", "bordered"), full_width = FALSE)
}
```

```{r ImportDataset, include=FALSE, warning=FALSE}
# Load the Dataset ----
library(readr)
course_evaluation_dataset <-
  read_csv(
    "data/10.b.BBT4206-End-Sem-20230821-20231128-BI2-BBIT4-2_WITHOUT_PII.csv",
    col_types = cols(
      `Submitted on:` = col_datetime(format = "%d/%m/%Y %H:%M"),
      Course = col_character(),
      Group = col_factor(levels = c(
                                    "20230821-20231128-BI2-BBIT4.2-A",
                                    "20230821-20231128-BI2-BBIT4.2-B",
                                    "20230821-20231128-BI2-BBIT4.2-C")),
      Gender = col_factor(levels = c("Male", "Female")),
      `Q01_Class Demographics` = col_factor(levels = c(
                                                       "1 : Group A - Regular",
                                                       "2 : Group A - Exempt",
                                                       "3 : Group B - Regular",
                                                       "4 : Group B - Exempt",
                                                       "5 : Group C - Regular",
                                                       "6 : Group C - Exempt"))
    )
  )
```

```{r evaluation_rating_per_question_per_group_per_gender, warning=FALSE, include=FALSE}
# Evaluation Rating per Group (1st) and per Gender (2nd) ----
## Average per Question per Group ----
evaluation_rating_per_question_per_group_per_gender <- course_evaluation_dataset %>%
  rename(`Class Group` = `Q01_Class Demographics`) %>%
  filter(!is.na(`Q02_General Questions->A - 11. I used the eLearning material posted`)) %>%
  rowwise() %>%
  
  # average_course_evaluation_rating
  mutate(average_course_evaluation_rating = mean(c(`Q02_General Questions->A - 1. I enjoyed the subject`, `Q02_General Questions->A - 2. Classes started and ended on time`, `Q02_General Questions->A - 3. The learning environment was participative, involved learning by doing and was group-based`, `Q02_General Questions->A - 4. The subject content was delivered according to the course outline and met my expectations`, `Q02_General Questions->A - 5. The topics were clear and logically developed`, `Q02_General Questions->A - 6. I developed my oral and writing skills`, `Q02_General Questions->A - 7. I developed my reflective and critical reasoning skills`, `Q02_General Questions->A - 8. The assessment methods assisted me to learn`, `Q02_General Questions->A - 9. I received relevant feedback`, `Q02_General Questions->A - 10. I read the recommended readings and notes`, `Q02_General Questions->A - 11. I used the eLearning material posted`))) %>%
  
  # average_level_of_learning_achieved
  mutate(average_level_of_learning_achieved = mean(c(`Q03_Level of Learning Achieved->B - 1. - BI1 - Concept 1 of 4: Ensemble Methods for Predictive Analytics`, `Q03_Level of Learning Achieved->B - 2. - BI1 - Concept 2 of 4: Linear Algorithms for Predictive Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 3. - BI1 - Concept 3 of 4: Non-Linear Algorithms for Predictive Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 4. - BI1 - Concept 4 of 4: Dashboarding for Business-Facing and Customer-Facing Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 1. - BI2 - Concept 1 of 4: Ensemble Methods for Predictive Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 2. - BI2 - Concept 2 of 4: Predictive Modelling Using R`,
                                                     `Q03_Level of Learning Achieved->B - 3. - BI2 - Concept 3 of 4: Data Warehousing and BI Strategy Implementation`,
                                                     `Q03_Level of Learning Achieved->B - 4. - BI2 - Concept 4 of 4: Data Engineering`))) %>%
  
  # average_level_of_skill_achieved
  mutate(average_level_of_skill_achieved = mean(c(`Q04_Competency for Technologies->D - 1. ChartJS`, `Q04_Competency for Technologies->D - 2. R (includes R markdown and R plumber)`, `Q04_Competency for Technologies->D - 3. MySQL`, `Q04_Competency for Technologies->D - 4. Kafka`, `Q04_Competency for Technologies->D - 5. ksqlDB`, `Q04_Competency for Technologies->D - 6. ClickHouse`, `Q04_Competency for Technologies->D - 7. Linear and Non-Linear ML Algorithms in the caret package`))) %>%

  # average_quality_of_teaching_strategies  
  mutate(average_quality_of_teaching_strategies = mean(c(`Q05_Quality of Teaching Strategies->E - 1. Group project`, `Q05_Quality of Teaching Strategies->E - 2. Lab manuals that outline the steps to follow during the labs`, `Q05_Quality of Teaching Strategies->E - 3. Required lab work submissions at the end of each lab manual that outline the activity to be done on your own`, `Q05_Quality of Teaching Strategies->E - 4. Supplementary videos/audio to watch/listen to`, `Q05_Quality of Teaching Strategies->E - 5. Lectures slides`, `Q05_Quality of Teaching Strategies->E - 6. Lecture notes on some of the lecture slides`, `Q05_Quality of Teaching Strategies->E - 7. The quality of the lectures given (quality measured by the breadth (the full span of knowledge of a subject) and depth (the extent to which specific topics are focused upon, amplified, and explored) of learning - NOT quality measured by how fun/comical the lectures are)`, `Q05_Quality of Teaching Strategies->E - 8. The division of theory and practice such that most of the theory is done during the recorded online classes and most of the practice is done during the physical classes`, `Q05_Quality of Teaching Strategies->E - 9. The recordings of online classes`))) %>%
  
  group_by(`Class Group`, `Gender`) %>%
  summarise(
    `A. I enjoyed the subject` =
      mean(`Q02_General Questions->A - 1. I enjoyed the subject`),
    `B. Classes started and ended on time` =
      mean(`Q02_General Questions->A - 2. Classes started and ended on time`),
    `C. The learning environment was participative, involved learning by doing and was group-based` =
      mean(`Q02_General Questions->A - 3. The learning environment was participative, involved learning by doing and was group-based`),
    `D. The subject content was delivered according to the course outline and met my expectations` =
      mean(`Q02_General Questions->A - 4. The subject content was delivered according to the course outline and met my expectations`),
    `E. The topics were clear and logically developed` =
      mean(`Q02_General Questions->A - 5. The topics were clear and logically developed`),
    `F. I developed my oral and writing skills` =
      mean(`Q02_General Questions->A - 6. I developed my oral and writing skills`),
    `G. I developed my reflective and critical reasoning skills` =
      mean(`Q02_General Questions->A - 7. I developed my reflective and critical reasoning skills`),
    `H. The assessment methods assisted me to learn` =
      mean(`Q02_General Questions->A - 8. The assessment methods assisted me to learn`),
    `I. I received relevant feedback` =
      mean(`Q02_General Questions->A - 9. I received relevant feedback`),
    `J. I read the recommended readings and notes` =
      mean(`Q02_General Questions->A - 10. I read the recommended readings and notes`),
    `K. I used the eLearning material posted` =
      mean(`Q02_General Questions->A - 11. I used the eLearning material posted`),
     `L. Average Quality of Teaching Strategies` =
      mean(average_quality_of_teaching_strategies),
     `M. Average Level of Learning Achieved` =
      mean(average_level_of_learning_achieved),
     `N. Average Level of Technical Skill Achieved` =
      mean(average_level_of_skill_achieved),
     `O. Average Course Evaluation Rating` =
      mean(average_course_evaluation_rating)
  ) %>%
  # If we had to sort the results
  # arrange(`Mean Average Course Evaluation Rating`) %>%
  select(
    `Class Group`,
    `Gender`,
    `A. I enjoyed the subject`,
    `B. Classes started and ended on time`,
    `C. The learning environment was participative, involved learning by doing and was group-based`,
    `D. The subject content was delivered according to the course outline and met my expectations`,
    `E. The topics were clear and logically developed`,
    `F. I developed my oral and writing skills`,
    `G. I developed my reflective and critical reasoning skills`,
    `H. The assessment methods assisted me to learn`,
    `I. I received relevant feedback`,
    `J. I read the recommended readings and notes`,
    `K. I used the eLearning material posted`,
    `L. Average Quality of Teaching Strategies`,
    `M. Average Level of Learning Achieved`,
    `N. Average Level of Technical Skill Achieved`,
    `O. Average Course Evaluation Rating`
  )
```

```{r OverallScore, include=FALSE}
overall_score <- course_evaluation_dataset %>%
  rename(`Class Group` = `Q01_Class Demographics`) %>%
  filter(!is.na(`Q02_General Questions->A - 11. I used the eLearning material posted`)) %>%
  rowwise() %>%
  
  # average_course_evaluation_rating
  mutate(average_course_evaluation_rating = mean(c(`Q02_General Questions->A - 1. I enjoyed the subject`, `Q02_General Questions->A - 2. Classes started and ended on time`, `Q02_General Questions->A - 3. The learning environment was participative, involved learning by doing and was group-based`, `Q02_General Questions->A - 4. The subject content was delivered according to the course outline and met my expectations`, `Q02_General Questions->A - 5. The topics were clear and logically developed`, `Q02_General Questions->A - 6. I developed my oral and writing skills`, `Q02_General Questions->A - 7. I developed my reflective and critical reasoning skills`, `Q02_General Questions->A - 8. The assessment methods assisted me to learn`, `Q02_General Questions->A - 9. I received relevant feedback`, `Q02_General Questions->A - 10. I read the recommended readings and notes`, `Q02_General Questions->A - 11. I used the eLearning material posted`))) %>%
  
  # average_level_of_learning_achieved
  mutate(average_level_of_learning_achieved = mean(c(`Q03_Level of Learning Achieved->B - 1. - BI1 - Concept 1 of 4: Ensemble Methods for Predictive Analytics`, `Q03_Level of Learning Achieved->B - 2. - BI1 - Concept 2 of 4: Linear Algorithms for Predictive Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 3. - BI1 - Concept 3 of 4: Non-Linear Algorithms for Predictive Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 4. - BI1 - Concept 4 of 4: Dashboarding for Business-Facing and Customer-Facing Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 1. - BI2 - Concept 1 of 4: Ensemble Methods for Predictive Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 2. - BI2 - Concept 2 of 4: Predictive Modelling Using R`,
                                                     `Q03_Level of Learning Achieved->B - 3. - BI2 - Concept 3 of 4: Data Warehousing and BI Strategy Implementation`,
                                                     `Q03_Level of Learning Achieved->B - 4. - BI2 - Concept 4 of 4: Data Engineering`))) %>%
  
  # average_level_of_skill_achieved
  mutate(average_level_of_skill_achieved = mean(c(`Q04_Competency for Technologies->D - 1. ChartJS`, `Q04_Competency for Technologies->D - 2. R (includes R markdown and R plumber)`, `Q04_Competency for Technologies->D - 3. MySQL`, `Q04_Competency for Technologies->D - 4. Kafka`, `Q04_Competency for Technologies->D - 5. ksqlDB`, `Q04_Competency for Technologies->D - 6. ClickHouse`, `Q04_Competency for Technologies->D - 7. Linear and Non-Linear ML Algorithms in the caret package`))) %>%

  # average_quality_of_teaching_strategies  
  mutate(average_quality_of_teaching_strategies = mean(c(`Q05_Quality of Teaching Strategies->E - 1. Group project`, `Q05_Quality of Teaching Strategies->E - 2. Lab manuals that outline the steps to follow during the labs`, `Q05_Quality of Teaching Strategies->E - 3. Required lab work submissions at the end of each lab manual that outline the activity to be done on your own`, `Q05_Quality of Teaching Strategies->E - 4. Supplementary videos/audio to watch/listen to`, `Q05_Quality of Teaching Strategies->E - 5. Lectures slides`, `Q05_Quality of Teaching Strategies->E - 6. Lecture notes on some of the lecture slides`, `Q05_Quality of Teaching Strategies->E - 7. The quality of the lectures given (quality measured by the breadth (the full span of knowledge of a subject) and depth (the extent to which specific topics are focused upon, amplified, and explored) of learning - NOT quality measured by how fun/comical the lectures are)`, `Q05_Quality of Teaching Strategies->E - 8. The division of theory and practice such that most of the theory is done during the recorded online classes and most of the practice is done during the physical classes`, `Q05_Quality of Teaching Strategies->E - 9. The recordings of online classes`))) %>%
  ungroup() %>%
  summarise(mean_score = mean(average_course_evaluation_rating), median_score = median(average_course_evaluation_rating)) %>%
  select(mean_score, median_score)

percentage_overall_score <- (overall_score$mean_score / 5) * 100

df <- data.frame(
  overall_score$mean_score,
  percentage_overall_score,
  overall_score$median_score
)
colnames(df) <- c("Mean Score", "Percentage", "Median Score")
```

# Course Evaluation Score

```{r TabularResultOfOverallScore, echo=FALSE, warning=FALSE, results='asis'}
formatted_mean_score <- sprintf("Mean Course Evaluation Score = %.4f", df$`Mean Score`)
cat(formatted_mean_score)
cat(" / 5")

formatted_percentage_mean_score <- sprintf("\n\nPercentage Mean Course Evaluation Score = %.2f", df$Percentage)
cat(formatted_percentage_mean_score)
cat("%")

formatted_median_score <- sprintf("\n\nMedian Course Evaluation Score = %.4f", df$`Median Score`)
cat(formatted_median_score)
cat(" / 5")
```

------------------------------------------------------------------------

```{r evaluation_rating_per_question_per_eLearning_class_per_gender, include=FALSE, warning=FALSE}
# Evaluation Rating per e-learning Class Group (1st) and per Gender (2nd) ----
# Get the average course evaluation rating per class group on e-learning
# (first grouping) and per gender (second grouping) 
evaluation_rating_per_question_per_eLearning_class_per_gender <- course_evaluation_dataset %>%
  rename(`Class Group` = `Q01_Class Demographics`) %>%
  filter(!is.na(`Q02_General Questions->A - 11. I used the eLearning material posted`)) %>%
  rowwise() %>%
  
  # average_course_evaluation_rating
  mutate(average_course_evaluation_rating = mean(c(`Q02_General Questions->A - 1. I enjoyed the subject`, `Q02_General Questions->A - 2. Classes started and ended on time`, `Q02_General Questions->A - 3. The learning environment was participative, involved learning by doing and was group-based`, `Q02_General Questions->A - 4. The subject content was delivered according to the course outline and met my expectations`, `Q02_General Questions->A - 5. The topics were clear and logically developed`, `Q02_General Questions->A - 6. I developed my oral and writing skills`, `Q02_General Questions->A - 7. I developed my reflective and critical reasoning skills`, `Q02_General Questions->A - 8. The assessment methods assisted me to learn`, `Q02_General Questions->A - 9. I received relevant feedback`, `Q02_General Questions->A - 10. I read the recommended readings and notes`, `Q02_General Questions->A - 11. I used the eLearning material posted`))) %>%
  
  # average_level_of_learning_achieved
  mutate(average_level_of_learning_achieved = mean(c(`Q03_Level of Learning Achieved->B - 1. - BI1 - Concept 1 of 4: Ensemble Methods for Predictive Analytics`, `Q03_Level of Learning Achieved->B - 2. - BI1 - Concept 2 of 4: Linear Algorithms for Predictive Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 3. - BI1 - Concept 3 of 4: Non-Linear Algorithms for Predictive Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 4. - BI1 - Concept 4 of 4: Dashboarding for Business-Facing and Customer-Facing Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 1. - BI2 - Concept 1 of 4: Ensemble Methods for Predictive Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 2. - BI2 - Concept 2 of 4: Predictive Modelling Using R`,
                                                     `Q03_Level of Learning Achieved->B - 3. - BI2 - Concept 3 of 4: Data Warehousing and BI Strategy Implementation`,
                                                     `Q03_Level of Learning Achieved->B - 4. - BI2 - Concept 4 of 4: Data Engineering`))) %>%
  
  # average_level_of_skill_achieved
  mutate(average_level_of_skill_achieved = mean(c(`Q04_Competency for Technologies->D - 1. ChartJS`, `Q04_Competency for Technologies->D - 2. R (includes R markdown and R plumber)`, `Q04_Competency for Technologies->D - 3. MySQL`, `Q04_Competency for Technologies->D - 4. Kafka`, `Q04_Competency for Technologies->D - 5. ksqlDB`, `Q04_Competency for Technologies->D - 6. ClickHouse`, `Q04_Competency for Technologies->D - 7. Linear and Non-Linear ML Algorithms in the caret package`))) %>%

  # average_quality_of_teaching_strategies  
  mutate(average_quality_of_teaching_strategies = mean(c(`Q05_Quality of Teaching Strategies->E - 1. Group project`, `Q05_Quality of Teaching Strategies->E - 2. Lab manuals that outline the steps to follow during the labs`, `Q05_Quality of Teaching Strategies->E - 3. Required lab work submissions at the end of each lab manual that outline the activity to be done on your own`, `Q05_Quality of Teaching Strategies->E - 4. Supplementary videos/audio to watch/listen to`, `Q05_Quality of Teaching Strategies->E - 5. Lectures slides`, `Q05_Quality of Teaching Strategies->E - 6. Lecture notes on some of the lecture slides`, `Q05_Quality of Teaching Strategies->E - 7. The quality of the lectures given (quality measured by the breadth (the full span of knowledge of a subject) and depth (the extent to which specific topics are focused upon, amplified, and explored) of learning - NOT quality measured by how fun/comical the lectures are)`, `Q05_Quality of Teaching Strategies->E - 8. The division of theory and practice such that most of the theory is done during the recorded online classes and most of the practice is done during the physical classes`, `Q05_Quality of Teaching Strategies->E - 9. The recordings of online classes`))) %>%
  
  group_by(`Group`, `Gender`) %>%
  summarise(
    `A. I enjoyed the subject` =
      mean(`Q02_General Questions->A - 1. I enjoyed the subject`),
    `B. Classes started and ended on time` =
      mean(`Q02_General Questions->A - 2. Classes started and ended on time`),
    `C. The learning environment was participative, involved learning by doing and was group-based` =
      mean(`Q02_General Questions->A - 3. The learning environment was participative, involved learning by doing and was group-based`),
    `D. The subject content was delivered according to the course outline and met my expectations` =
      mean(`Q02_General Questions->A - 4. The subject content was delivered according to the course outline and met my expectations`),
    `E. The topics were clear and logically developed` =
      mean(`Q02_General Questions->A - 5. The topics were clear and logically developed`),
    `F. I developed my oral and writing skills` =
      mean(`Q02_General Questions->A - 6. I developed my oral and writing skills`),
    `G. I developed my reflective and critical reasoning skills` =
      mean(`Q02_General Questions->A - 7. I developed my reflective and critical reasoning skills`),
    `H. The assessment methods assisted me to learn` =
      mean(`Q02_General Questions->A - 8. The assessment methods assisted me to learn`),
    `I. I received relevant feedback` =
      mean(`Q02_General Questions->A - 9. I received relevant feedback`),
    `J. I read the recommended readings and notes` =
      mean(`Q02_General Questions->A - 10. I read the recommended readings and notes`),
    `K. I used the eLearning material posted` =
      mean(`Q02_General Questions->A - 11. I used the eLearning material posted`),
     `L. Average Quality of Teaching Strategies` =
      mean(average_quality_of_teaching_strategies),
     `M. Average Level of Learning Achieved` =
      mean(average_level_of_learning_achieved),
     `N. Average Level of Technical Skill Achieved` =
      mean(average_level_of_skill_achieved),
     `O. Average Course Evaluation Rating` =
      mean(average_course_evaluation_rating)
  ) %>%
  # If we had to sort the results
  # arrange(`O. Average Course Evaluation Rating`) %>%
  select(
    `Group`,
    `Gender`,
    `A. I enjoyed the subject`,
    `B. Classes started and ended on time`,
    `C. The learning environment was participative, involved learning by doing and was group-based`,
    `D. The subject content was delivered according to the course outline and met my expectations`,
    `E. The topics were clear and logically developed`,
    `F. I developed my oral and writing skills`,
    `G. I developed my reflective and critical reasoning skills`,
    `H. The assessment methods assisted me to learn`,
    `I. I received relevant feedback`,
    `J. I read the recommended readings and notes`,
    `K. I used the eLearning material posted`,
    `L. Average Quality of Teaching Strategies`,
    `M. Average Level of Learning Achieved`,
    `N. Average Level of Technical Skill Achieved`,
    `O. Average Course Evaluation Rating`
  )
```

```{r evaluation_rating_per_question_per_gender_per_group, include=FALSE, warning=FALSE}
# Evaluation Rating per Gender (1st) and per Group (2nd) ----
# The average course evaluation rating per gender (first grouping) and per
# group (second grouping)
evaluation_rating_per_question_per_gender_per_group <- course_evaluation_dataset %>%
  rename(`Class Group` = `Q01_Class Demographics`) %>%
  filter(!is.na(`Q02_General Questions->A - 11. I used the eLearning material posted`)) %>%
  rowwise() %>%
  
  # average_course_evaluation_rating
  mutate(average_course_evaluation_rating = mean(c(`Q02_General Questions->A - 1. I enjoyed the subject`, `Q02_General Questions->A - 2. Classes started and ended on time`, `Q02_General Questions->A - 3. The learning environment was participative, involved learning by doing and was group-based`, `Q02_General Questions->A - 4. The subject content was delivered according to the course outline and met my expectations`, `Q02_General Questions->A - 5. The topics were clear and logically developed`, `Q02_General Questions->A - 6. I developed my oral and writing skills`, `Q02_General Questions->A - 7. I developed my reflective and critical reasoning skills`, `Q02_General Questions->A - 8. The assessment methods assisted me to learn`, `Q02_General Questions->A - 9. I received relevant feedback`, `Q02_General Questions->A - 10. I read the recommended readings and notes`, `Q02_General Questions->A - 11. I used the eLearning material posted`))) %>%
  
  # average_level_of_learning_achieved
  mutate(average_level_of_learning_achieved = mean(c(`Q03_Level of Learning Achieved->B - 1. - BI1 - Concept 1 of 4: Ensemble Methods for Predictive Analytics`, `Q03_Level of Learning Achieved->B - 2. - BI1 - Concept 2 of 4: Linear Algorithms for Predictive Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 3. - BI1 - Concept 3 of 4: Non-Linear Algorithms for Predictive Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 4. - BI1 - Concept 4 of 4: Dashboarding for Business-Facing and Customer-Facing Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 1. - BI2 - Concept 1 of 4: Ensemble Methods for Predictive Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 2. - BI2 - Concept 2 of 4: Predictive Modelling Using R`,
                                                     `Q03_Level of Learning Achieved->B - 3. - BI2 - Concept 3 of 4: Data Warehousing and BI Strategy Implementation`,
                                                     `Q03_Level of Learning Achieved->B - 4. - BI2 - Concept 4 of 4: Data Engineering`))) %>%

  # average_level_of_skill_achieved
  mutate(average_level_of_skill_achieved = mean(c(`Q04_Competency for Technologies->D - 1. ChartJS`, `Q04_Competency for Technologies->D - 2. R (includes R markdown and R plumber)`, `Q04_Competency for Technologies->D - 3. MySQL`, `Q04_Competency for Technologies->D - 4. Kafka`, `Q04_Competency for Technologies->D - 5. ksqlDB`, `Q04_Competency for Technologies->D - 6. ClickHouse`, `Q04_Competency for Technologies->D - 7. Linear and Non-Linear ML Algorithms in the caret package`))) %>%

  # average_quality_of_teaching_strategies  
  mutate(average_quality_of_teaching_strategies = mean(c(`Q05_Quality of Teaching Strategies->E - 1. Group project`, `Q05_Quality of Teaching Strategies->E - 2. Lab manuals that outline the steps to follow during the labs`, `Q05_Quality of Teaching Strategies->E - 3. Required lab work submissions at the end of each lab manual that outline the activity to be done on your own`, `Q05_Quality of Teaching Strategies->E - 4. Supplementary videos/audio to watch/listen to`, `Q05_Quality of Teaching Strategies->E - 5. Lectures slides`, `Q05_Quality of Teaching Strategies->E - 6. Lecture notes on some of the lecture slides`, `Q05_Quality of Teaching Strategies->E - 7. The quality of the lectures given (quality measured by the breadth (the full span of knowledge of a subject) and depth (the extent to which specific topics are focused upon, amplified, and explored) of learning - NOT quality measured by how fun/comical the lectures are)`, `Q05_Quality of Teaching Strategies->E - 8. The division of theory and practice such that most of the theory is done during the recorded online classes and most of the practice is done during the physical classes`, `Q05_Quality of Teaching Strategies->E - 9. The recordings of online classes`))) %>%

  group_by(`Gender`, `Class Group`) %>%
  summarise(
    `A. I enjoyed the subject` =
      mean(`Q02_General Questions->A - 1. I enjoyed the subject`),
    `B. Classes started and ended on time` =
      mean(`Q02_General Questions->A - 2. Classes started and ended on time`),
    `C. The learning environment was participative, involved learning by doing and was group-based` =
      mean(`Q02_General Questions->A - 3. The learning environment was participative, involved learning by doing and was group-based`),
    `D. The subject content was delivered according to the course outline and met my expectations` =
      mean(`Q02_General Questions->A - 4. The subject content was delivered according to the course outline and met my expectations`),
    `E. The topics were clear and logically developed` =
      mean(`Q02_General Questions->A - 5. The topics were clear and logically developed`),
    `F. I developed my oral and writing skills` =
      mean(`Q02_General Questions->A - 6. I developed my oral and writing skills`),
    `G. I developed my reflective and critical reasoning skills` =
      mean(`Q02_General Questions->A - 7. I developed my reflective and critical reasoning skills`),
    `H. The assessment methods assisted me to learn` =
      mean(`Q02_General Questions->A - 8. The assessment methods assisted me to learn`),
    `I. I received relevant feedback` =
      mean(`Q02_General Questions->A - 9. I received relevant feedback`),
    `J. I read the recommended readings and notes` =
      mean(`Q02_General Questions->A - 10. I read the recommended readings and notes`),
    `K. I used the eLearning material posted` =
      mean(`Q02_General Questions->A - 11. I used the eLearning material posted`),
     `L. Average Quality of Teaching Strategies` =
      mean(average_quality_of_teaching_strategies),
     `M. Average Level of Learning Achieved` =
      mean(average_level_of_learning_achieved),
     `N. Average Level of Technical Skill Achieved` =
      mean(average_level_of_skill_achieved),
     `O. Average Course Evaluation Rating` =
      mean(average_course_evaluation_rating)
  ) %>%
  # If we had to sort the results
  # arrange(`O. Average Course Evaluation Rating`) %>%
  select(
    `Class Group`,
    `Gender`,
    `A. I enjoyed the subject`,
    `B. Classes started and ended on time`,
    `C. The learning environment was participative, involved learning by doing and was group-based`,
    `D. The subject content was delivered according to the course outline and met my expectations`,
    `E. The topics were clear and logically developed`,
    `F. I developed my oral and writing skills`,
    `G. I developed my reflective and critical reasoning skills`,
    `H. The assessment methods assisted me to learn`,
    `I. I received relevant feedback`,
    `J. I read the recommended readings and notes`,
    `K. I used the eLearning material posted`,
    `L. Average Quality of Teaching Strategies`,
    `M. Average Level of Learning Achieved`,
    `N. Average Level of Technical Skill Achieved`,
    `O. Average Course Evaluation Rating`
  )
```

```{r Transpose, include=FALSE, warning=FALSE}
# Transpose the Data  for Easier Visualization ----
# We then transpose the data frame (for the group by class group and group by gender options)

# Group by Class Group
evaluation_rating_per_question_per_group_long_data <- evaluation_rating_per_question_per_group_per_gender %>%
  select(-`Gender`) %>%
  pivot_longer(
               cols = -`Class Group`,
               names_to = "Evaluation Question",
               values_to = "Mean Value")

# Group by eLearning Class
evaluation_rating_per_question_per_class_long_data <- evaluation_rating_per_question_per_eLearning_class_per_gender %>%
  select(-`Gender`) %>%
  pivot_longer(
               cols = -`Group`,
               names_to = "Evaluation Question",
               values_to = "Mean Value")

# Group by Gender
evaluation_rating_per_question_per_gender_long_data <- evaluation_rating_per_question_per_gender_per_group %>%
  select(-`Class Group`) %>%
  pivot_longer(
               cols = -`Gender`,
               names_to = "Evaluation Question",
               values_to = "Mean Value")
```

\newpage

# Quantitative Data Analysis

## Course Evaluation Scores per Group

```{r ProcessStringsBeforePlotting, warning=FALSE, include=FALSE}
# This is done to enable word wrapping when the plot is created
# Per Group
evaluation_rating_per_question_per_group_long_data$`Evaluation Question` <- 
  str_wrap(evaluation_rating_per_question_per_group_long_data$`Evaluation Question`, # nolint
         width = 30)

# Per e-Learning Class
evaluation_rating_per_question_per_class_long_data$`Evaluation Question` <- 
  str_wrap(evaluation_rating_per_question_per_class_long_data$`Evaluation Question`, # nolint
         width = 30)

# Per Gender
evaluation_rating_per_question_per_gender_long_data$`Evaluation Question` <- 
  str_wrap(evaluation_rating_per_question_per_gender_long_data$`Evaluation Question`, # nolint
         width = 30)
```

The **"Average Course Evaluation Rating"** variable in the plot below indicates the score **per group** with a baseline of 4/5.

```{r VisualizationsForCourseEvaluationResultsperClassGroup, echo=FALSE, fig.height=10, warning=FALSE}
### Visualizations (Grouped Vertical Bar Chart) ----
# Per Group
ggplot(evaluation_rating_per_question_per_class_long_data,
       aes(fill = `Group`, y = `Mean Value`, x = `Evaluation Question`,
           label = `Mean Value`)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_flip() +  # Flip the coordinates to make it vertical
  labs(title = "Standard Course Evaluation Score per Question per Group",
       x = "Standard Course Evaluation Questions", y = "Mean Value") +
  scale_fill_manual(values = blue_grey_colours_3) +
  blue_grey_theme() +
  geom_hline(yintercept = 4, color = "#b90c0c",
             linetype = "dashed", size = 1)
```

\newpage

The **"Average Course Evaluation Rating"** variable in the plot below indicates the score **per gender** with a baseline of 4/5.

```{r VisualizationsForCourseEvaluationResultsperGender, echo=FALSE, fig.height=12, warning=FALSE}
### Visualizations (Grouped Vertical Bar Chart) ----
# Per Group
ggplot(evaluation_rating_per_question_per_gender_long_data,
       aes(fill = `Gender`, y = `Mean Value`, x = `Evaluation Question`,
           label = `Mean Value`)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_flip() +  # Flip the coordinates to make it vertical
  labs(title = "Standard Course Evaluation Score per Question per Gender",
       x = "Standard Course Evaluation Questions", y = "Mean Value") +
  scale_fill_manual(values = blue_grey_colours_2) +
  blue_grey_theme() +
  geom_hline(yintercept = 4, color = "#b90c0c",
             linetype = "dashed", size = 1)
```

\newpage

The plot below presents a drill-down of the class group into **regular and exempt** students:

```{r VisualizationsForCourseEvaluationResultsperGroup, echo=FALSE, fig.height=12, warning=FALSE}
### Visualizations (Grouped Vertical Bar Chart) ----
# Per Group
ggplot(evaluation_rating_per_question_per_group_long_data,
       aes(fill = `Class Group`, y = `Mean Value`, x = `Evaluation Question`,
           label = `Mean Value`)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_flip() +  # Flip the coordinates to make it vertical
  labs(title = "Standard Course Evaluation Score per Question per Gender",
       x = "Standard Course Evaluation Questions", y = "Mean Value") +
  scale_fill_manual(values = blue_grey_colours_6) +
  blue_grey_theme() +
  geom_hline(yintercept = 4, color = "#b90c0c",
             linetype = "dashed", size = 1)



```

\newpage

Note that the 22 indicated as "NA" are all in Group A. Group A students filled in the course evaluation form before the question was set. Out of those asked, 98% do not regret the choice to take the Business Intelligence Option instead of the Computer Networking Option in their final year.

```{r Regret, echo=FALSE, message=FALSE, warning=FALSE}
regret <- course_evaluation_dataset %>%
  group_by(`Q07_Regret->G - 1. Do you regret choosing the BI Option instead of the Computer Networking Option?`) %>%
  summarise(Number = n()) %>%
  rename(`Do you regret choosing the BI Option?` = `Q07_Regret->G - 1. Do you regret choosing the BI Option instead of the Computer Networking Option?`)
regret
```

\newpage

## Correlations

```{r CorrelationMatrixWithoutFigures, fig.height=10, include=FALSE}
# The general correlation values are presented below:
course_evaluation_dataset_short_names <- course_evaluation_dataset %>%
  rename(
    `A. Enjoying Subject` = `Q02_General Questions->A - 1. I enjoyed the subject`,
    `B. Classes Start-End` = `Q02_General Questions->A - 2. Classes started and ended on time`,
    `C. Learning Environment` = `Q02_General Questions->A - 3. The learning environment was participative, involved learning by doing and was group-based`,
    `D. Content Delivery` = `Q02_General Questions->A - 4. The subject content was delivered according to the course outline and met my expectations`,
    `E. Clear Topics` = `Q02_General Questions->A - 5. The topics were clear and logically developed`,
     `F. Oral and Writing` = `Q02_General Questions->A - 6. I developed my oral and writing skills`,
    `G. Critical Thinking` = `Q02_General Questions->A - 7. I developed my reflective and critical reasoning skills`,
     `H. Assessment Methods` = `Q02_General Questions->A - 8. The assessment methods assisted me to learn`,
    `I. Relevant Feedback` = `Q02_General Questions->A - 9. I received relevant feedback`,
    `J. Read Recommendations` = `Q02_General Questions->A - 10. I read the recommended readings and notes`,
    `L. eLearning Material` = `Q02_General Questions->A - 11. I used the eLearning material posted`,
    `Understood BI1 Concept 1` = `Q03_Level of Learning Achieved->B - 1. - BI1 - Concept 1 of 4: Ensemble Methods for Predictive Analytics`,
    `Understood BI1 Concept 2` = `Q03_Level of Learning Achieved->B - 2. - BI1 - Concept 2 of 4: Linear Algorithms for Predictive Analytics`,
    `Understood BI1 Concept 3` = `Q03_Level of Learning Achieved->B - 3. - BI1 - Concept 3 of 4: Non-Linear Algorithms for Predictive Analytics`,
    `Understood BI1 Concept 4` = `Q03_Level of Learning Achieved->B - 4. - BI1 - Concept 4 of 4: Dashboarding for Business-Facing and Customer-Facing Analytics`,
    `Understood BI2 Concept 1` = `Q03_Level of Learning Achieved->B - 1. - BI2 - Concept 1 of 4: Ensemble Methods for Predictive Analytics`,
    `Understood BI2 Concept 2` = `Q03_Level of Learning Achieved->B - 2. - BI2 - Concept 2 of 4: Predictive Modelling Using R`,
    `Understood BI2 Concept 3` = `Q03_Level of Learning Achieved->B - 3. - BI2 - Concept 3 of 4: Data Warehousing and BI Strategy Implementation`,
    `Understood BI2 Concept 4` = `Q03_Level of Learning Achieved->B - 4. - BI2 - Concept 4 of 4: Data Engineering`,
    
    `Acquired Skill 1` = `Q04_Competency for Technologies->D - 1. ChartJS`,
    `Acquired Skill 2` = `Q04_Competency for Technologies->D - 2. R (includes R markdown and R plumber)`,
    `Acquired Skill 3` = `Q04_Competency for Technologies->D - 3. MySQL`,
    `Acquired Skill 4` = `Q04_Competency for Technologies->D - 4. Kafka`,
    
    `Acquired Skill 5` = `Q04_Competency for Technologies->D - 5. ksqlDB`,
    `Acquired Skill 6` = `Q04_Competency for Technologies->D - 6. ClickHouse`,
    `Acquired Skill 7` = `Q04_Competency for Technologies->D - 7. Linear and Non-Linear ML Algorithms in the caret package`,
    
    `Group Project` = `Q05_Quality of Teaching Strategies->E - 1. Group project`,
    `Labs Manuals` = `Q05_Quality of Teaching Strategies->E - 2. Lab manuals that outline the steps to follow during the labs`,
    `Lab Submissions` = `Q05_Quality of Teaching Strategies->E - 3. Required lab work submissions at the end of each lab manual that outline the activity to be done on your own`,
    `Supplementary Videos/Audio` = `Q05_Quality of Teaching Strategies->E - 4. Supplementary videos/audio to watch/listen to`,
    `Lecture Slides` = `Q05_Quality of Teaching Strategies->E - 5. Lectures slides`,
    `Lecture Notes` = `Q05_Quality of Teaching Strategies->E - 6. Lecture notes on some of the lecture slides`,
    `Quality of Lectures` = `Q05_Quality of Teaching Strategies->E - 7. The quality of the lectures given (quality measured by the breadth (the full span of knowledge of a subject) and depth (the extent to which specific topics are focused upon, amplified, and explored) of learning - NOT quality measured by how fun/comical the lectures are)`,
    `Online for Theory` = `Q05_Quality of Teaching Strategies->E - 8. The division of theory and practice such that most of the theory is done during the recorded online classes and most of the practice is done during the physical classes`,
    `Recording of Online` = `Q05_Quality of Teaching Strategies->E - 9. The recordings of online classes`
    ) %>%
  select(
    `Absenteeism`,
    `A. Enjoying Subject`,
    `B. Classes Start-End`,
    `C. Learning Environment`,
    `D. Content Delivery`,
    `E. Clear Topics`,
    `F. Oral and Writing`,
    `G. Critical Thinking`,
    `H. Assessment Methods`,
    `I. Relevant Feedback`,
    `J. Read Recommendations`,
    `L. eLearning Material`,
    `Understood BI1 Concept 1`,
    `Understood BI1 Concept 2`,
    `Understood BI1 Concept 3`,
    `Understood BI1 Concept 4`,
    `Understood BI2 Concept 1`,
    `Understood BI2 Concept 2`,
    `Understood BI2 Concept 3`,
    `Understood BI2 Concept 4`,
    `Acquired Skill 1`,
    `Acquired Skill 2`,
    `Acquired Skill 3`,
    `Acquired Skill 4`,
    `Acquired Skill 5`,
    `Acquired Skill 6`,
    `Acquired Skill 7`,
    `Group Project`,
    `Labs Manuals`,
    `Lab Submissions`,
    `Supplementary Videos/Audio`,
    `Lecture Slides`,
    `Lecture Notes`,
    `Quality of Lectures`,
    `Online for Theory`,
    `Recording of Online`
    
  )

# ggcorrplot(cor(course_evaluation_dataset_short_names))

```

The specific correlation values are presented below:

```{r CorrelationMatrixWithFigures, echo=FALSE, fig.height=12, fig.width=12}
# Create a correlation matrix
corr_matrix <- cor(course_evaluation_dataset_short_names)

# Create a ggplot2 plot for the correlation matrix
p <- ggplot2::ggplot(data = reshape2::melt(corr_matrix),
                     ggplot2::aes(Var1, Var2, fill = value)) +
  ggplot2::geom_tile() +
  ggplot2::geom_text(ggplot2::aes(label = label_wrap(label, width = 6)), size = 4) +  # Customize label_wrap width
  ggplot2::scale_fill_gradient2(low = "red", high = "green") +
  ggplot2::theme_minimal() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1))

ggcorrplot(lab_size = 2, corr_matrix, hc.order = TRUE, type = "lower", lab = TRUE)
```

### Interesting Correlations

The following are hypothetical statements given that "correlation does not imply causation".

-   **.81 correlation** between "Acquired Skill 6 (ClickHouse)" and "Acquired Skill 5 (ksqlDB)": *The two technologies are related and taught in the same lab (Data Engineering).*

-   **.82 correlation** between "Acquired Skill 4 (Kafka)" and "Acquired Skill 5 (ksqlDB)": *The two technologies are related and taught in the same lab and concept (Data Engineering).*

-   **.78 correlation** between "Acquired Skill 6 (ClickHouse)" and "Acquired Skill 4 (Kafka)": *The two technologies are related and taught in the same lab (Data Engineering).*

-   **.75 correlation** between "Lab Manuals (Lab manuals that outline the steps to follow during the labs)" and "Lab Submissions (Required lab work submissions at the end of each lab manual that outline the activity to be done on your own)": *The more the effort to clearly outline the steps to be done in a lab manual, the more impact it has on the students' learning.*

-   **.76 correlation** between "The quality of lecture slides" and "the quality of lecture notes on some of the slides: *The higher the quality of the slides, the higher the quality of the notes on some of the slides.*

(1) A **.76 correlation** between "The quality of lecture slides" and "the quality of lecture notes on some of the slides.

```{r DrillDownCorr1, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(course_evaluation_dataset,
       aes(x = `Q05_Quality of Teaching Strategies->E - 5. Lectures slides`, y = `Q05_Quality of Teaching Strategies->E - 6. Lecture notes on some of the lecture slides`, shape = Gender, color = Gender)) +
  geom_point() +
  geom_smooth(method = lm)
```

\newpage

(2) A **.75 correlation** between "Lab Manuals (Lab manuals that outline the steps to follow during the labs)" and "Lab Submissions (Required lab work submissions at the end of each lab manual that outline the activity to be done on your own)".

```{r DrillDownCorr2, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(course_evaluation_dataset,
       aes(x = `Q05_Quality of Teaching Strategies->E - 2. Lab manuals that outline the steps to follow during the labs`, y = `Q05_Quality of Teaching Strategies->E - 3. Required lab work submissions at the end of each lab manual that outline the activity to be done on your own`, shape = Gender, color = Gender)) +
  geom_point() +
  geom_smooth(method = lm)
```

\newpage

### Absenteeism Percentage

The lower the absenteeism, the more a student makes use of the lab manuals for practical classes. And the more a student makes use of the lab manuals, the more the lab submissions have an impact on their overall acquisition of skills.

With this in mind, a further investigation of the **absenteeism percentage** is presented below.

#### Absenteeism by General Class Group

```{r AbsenteeismBoxandWhiskerGroup, echo=FALSE, fig.height=5, fig.width=15, message=FALSE, warning=FALSE}
featurePlot(x = course_evaluation_dataset$Absenteeism, y = course_evaluation_dataset$Group, plot = "box")
```

#### Absenteeism by Specific Class Group

```{r AbsenteeismBoxandWhiskerSpecificGroup, echo=FALSE, fig.height=5, fig.width=15, message=FALSE, warning=FALSE}
featurePlot(x = course_evaluation_dataset$Absenteeism, y = course_evaluation_dataset$`Q01_Class Demographics`, plot = "box")
```

#### Absenteeism by Gender

```{r AbsenteeismBoxandWhiskerGender, echo=FALSE, fig.height=5, fig.width=15, message=FALSE, warning=FALSE}
featurePlot(x = course_evaluation_dataset$Absenteeism, y = course_evaluation_dataset$Gender, plot = "box")
```

\newpage

# Qualitative Data Analysis

```{r QualitativeDatareProcessing, message=FALSE, warning=FALSE, include=FALSE}
## Average per Question per Group ----
evaluation_likes_and_wishes <- course_evaluation_dataset %>%
  rename(`Class Group` = `Q01_Class Demographics`) %>%
  rename(`Likes` = `Q07_Likes->G - 1. Write two things you liked about the teaching and learning in this course.`) %>%
  rename(`Wishes` = `Q07_Wishes->G - 2. Write at least one recommendation to improve the teaching and learning in this course (for future classes)`) %>%
  rename(`Topics` = `Q06_Topics to Add->F - 1. Are there any topics that you recommend should be added to in addition to the ones already in the BI1 and BI2 course outlines?`) %>%
  filter(!is.na(`Q02_General Questions->A - 11. I used the eLearning material posted`)) %>%
  rowwise() %>%
  
  # average_course_evaluation_rating
  mutate(average_course_evaluation_rating = mean(c(`Q02_General Questions->A - 1. I enjoyed the subject`, `Q02_General Questions->A - 2. Classes started and ended on time`, `Q02_General Questions->A - 3. The learning environment was participative, involved learning by doing and was group-based`, `Q02_General Questions->A - 4. The subject content was delivered according to the course outline and met my expectations`, `Q02_General Questions->A - 5. The topics were clear and logically developed`, `Q02_General Questions->A - 6. I developed my oral and writing skills`, `Q02_General Questions->A - 7. I developed my reflective and critical reasoning skills`, `Q02_General Questions->A - 8. The assessment methods assisted me to learn`, `Q02_General Questions->A - 9. I received relevant feedback`, `Q02_General Questions->A - 10. I read the recommended readings and notes`, `Q02_General Questions->A - 11. I used the eLearning material posted`))) %>%
  
  # average_level_of_learning_achieved
  mutate(average_level_of_learning_achieved = mean(c(`Q03_Level of Learning Achieved->B - 1. - BI1 - Concept 1 of 4: Ensemble Methods for Predictive Analytics`, `Q03_Level of Learning Achieved->B - 2. - BI1 - Concept 2 of 4: Linear Algorithms for Predictive Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 3. - BI1 - Concept 3 of 4: Non-Linear Algorithms for Predictive Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 4. - BI1 - Concept 4 of 4: Dashboarding for Business-Facing and Customer-Facing Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 1. - BI2 - Concept 1 of 4: Ensemble Methods for Predictive Analytics`,
                                                     `Q03_Level of Learning Achieved->B - 2. - BI2 - Concept 2 of 4: Predictive Modelling Using R`,
                                                     `Q03_Level of Learning Achieved->B - 3. - BI2 - Concept 3 of 4: Data Warehousing and BI Strategy Implementation`,
                                                     `Q03_Level of Learning Achieved->B - 4. - BI2 - Concept 4 of 4: Data Engineering`))) %>%
  
  # average_level_of_skill_achieved
  mutate(average_level_of_skill_achieved = mean(c(`Q04_Competency for Technologies->D - 1. ChartJS`, `Q04_Competency for Technologies->D - 2. R (includes R markdown and R plumber)`, `Q04_Competency for Technologies->D - 3. MySQL`, `Q04_Competency for Technologies->D - 4. Kafka`, `Q04_Competency for Technologies->D - 5. ksqlDB`, `Q04_Competency for Technologies->D - 6. ClickHouse`, `Q04_Competency for Technologies->D - 7. Linear and Non-Linear ML Algorithms in the caret package`))) %>%

  # average_quality_of_teaching_strategies  
  mutate(average_quality_of_teaching_strategies = mean(c(`Q05_Quality of Teaching Strategies->E - 1. Group project`, `Q05_Quality of Teaching Strategies->E - 2. Lab manuals that outline the steps to follow during the labs`, `Q05_Quality of Teaching Strategies->E - 3. Required lab work submissions at the end of each lab manual that outline the activity to be done on your own`, `Q05_Quality of Teaching Strategies->E - 4. Supplementary videos/audio to watch/listen to`, `Q05_Quality of Teaching Strategies->E - 5. Lectures slides`, `Q05_Quality of Teaching Strategies->E - 6. Lecture notes on some of the lecture slides`, `Q05_Quality of Teaching Strategies->E - 7. The quality of the lectures given (quality measured by the breadth (the full span of knowledge of a subject) and depth (the extent to which specific topics are focused upon, amplified, and explored) of learning - NOT quality measured by how fun/comical the lectures are)`, `Q05_Quality of Teaching Strategies->E - 8. The division of theory and practice such that most of the theory is done during the recorded online classes and most of the practice is done during the physical classes`, `Q05_Quality of Teaching Strategies->E - 9. The recordings of online classes`))) %>%
  
    rename(
    `A. I enjoyed the subject` =
      (`Q02_General Questions->A - 1. I enjoyed the subject`),
    `B. Classes started and ended on time` =
      (`Q02_General Questions->A - 2. Classes started and ended on time`),
    `C. The learning environment was participative, involved learning by doing and was group-based` =
      (`Q02_General Questions->A - 3. The learning environment was participative, involved learning by doing and was group-based`),
    `D. The subject content was delivered according to the course outline and met my expectations` =
      (`Q02_General Questions->A - 4. The subject content was delivered according to the course outline and met my expectations`),
    `E. The topics were clear and logically developed` =
      (`Q02_General Questions->A - 5. The topics were clear and logically developed`),
    `F. I developed my oral and writing skills` =
      (`Q02_General Questions->A - 6. I developed my oral and writing skills`),
    `G. I developed my reflective and critical reasoning skills` =
      (`Q02_General Questions->A - 7. I developed my reflective and critical reasoning skills`),
    `H. The assessment methods assisted me to learn` =
      (`Q02_General Questions->A - 8. The assessment methods assisted me to learn`),
    `I. I received relevant feedback` =
      (`Q02_General Questions->A - 9. I received relevant feedback`),
    `J. I read the recommended readings and notes` =
      (`Q02_General Questions->A - 10. I read the recommended readings and notes`),
    `K. I used the eLearning material posted` =
      (`Q02_General Questions->A - 11. I used the eLearning material posted`),
     `L. Average Quality of Teaching Strategies` =
      (average_quality_of_teaching_strategies),
     `M. Average Level of Learning Achieved` =
      (average_level_of_learning_achieved),
     `N. Average Level of Technical Skill Achieved` =
      (average_level_of_skill_achieved),
     `O. Average Course Evaluation Rating` =
      (average_course_evaluation_rating)
  ) %>%
  
  group_by(`Class Group`, `Gender`) %>%
  # If we had to sort the results
  arrange(`O. Average Course Evaluation Rating`) %>%
  select(
    `Class Group`,
    `Gender`,
    `A. I enjoyed the subject`,
    `B. Classes started and ended on time`,
    `C. The learning environment was participative, involved learning by doing and was group-based`,
    `D. The subject content was delivered according to the course outline and met my expectations`,
    `E. The topics were clear and logically developed`,
    `F. I developed my oral and writing skills`,
    `G. I developed my reflective and critical reasoning skills`,
    `H. The assessment methods assisted me to learn`,
    `I. I received relevant feedback`,
    `J. I read the recommended readings and notes`,
    `K. I used the eLearning material posted`,
    `L. Average Quality of Teaching Strategies`,
    `M. Average Level of Learning Achieved`,
    `N. Average Level of Technical Skill Achieved`,
    `O. Average Course Evaluation Rating`,
    `Likes`,
    `Wishes`,
    `Topics`
  )


expand_contractions <- function(doc) {
  doc <- gsub("I'm", "I am", doc, ignore.case = TRUE)
  doc <- gsub("you're", "you are", doc, ignore.case = TRUE)
  doc <- gsub("he's", "he is", doc, ignore.case = TRUE)
  doc <- gsub("she's", "she is", doc, ignore.case = TRUE)
  doc <- gsub("it's", "it is", doc, ignore.case = TRUE)
  doc <- gsub("we're", "we are", doc, ignore.case = TRUE)
  doc <- gsub("they're", "they are", doc, ignore.case = TRUE)
  doc <- gsub("I'll", "I will", doc, ignore.case = TRUE)
  doc <- gsub("you'll", "you will", doc, ignore.case = TRUE)
  doc <- gsub("he'll", "he will", doc, ignore.case = TRUE)
  doc <- gsub("she'll", "she will", doc, ignore.case = TRUE)
  doc <- gsub("it'll", "it will", doc, ignore.case = TRUE)
  doc <- gsub("we'll", "we will", doc, ignore.case = TRUE)
  doc <- gsub("they'll", "they will", doc, ignore.case = TRUE)
  doc <- gsub("won't", "will not", doc, ignore.case = TRUE)
  doc <- gsub("can't", "cannot", doc, ignore.case = TRUE)
  doc <- gsub("n't", " not", doc, ignore.case = TRUE)
  return(doc)
}

# Expand contractions
evaluation_likes_and_wishes$Likes <- sapply(evaluation_likes_and_wishes$Likes, expand_contractions)

evaluation_likes_and_wishes$Wishes <- sapply(evaluation_likes_and_wishes$Wishes, expand_contractions)

# Remove special characters
remove_special_characters <- function(doc) {
  gsub("[^a-zA-Z ]", "", doc, ignore.case = TRUE)
}

evaluation_likes_and_wishes$Likes <- sapply(evaluation_likes_and_wishes$Likes, remove_special_characters)

evaluation_likes_and_wishes$Wishes <- sapply(evaluation_likes_and_wishes$Wishes, remove_special_characters)

evaluation_likes_and_wishes$Topics <- sapply(evaluation_likes_and_wishes$Topics, remove_special_characters)

# Tokenization, stopword removal, censorship, short word removal
undesirable_words <- c("wow", "lol", "none", "na")

evaluation_likes_filtered <- evaluation_likes_and_wishes %>%
  # We start by tokenization (un-nesting words). This is from the variable
  # "Like" into the variable "word".
  unnest_tokens(word, Likes, token = "ngrams", n = 1) %>%
  # Then we remove stopwords using an anti-join
  # Anti-join: do not join where the word is in the list of stopwords
  anti_join(stop_words, by = c("word")) %>%
  distinct() %>%
  # Censor or filter out unwanted words
  filter(!word %in% undesirable_words) %>%
  # Include only words that are more than 3 characters long (assuming that
  # these are the words that are meaningful)
  filter(nchar(word) > 3) %>%
  # We then rename the variable "word" for ease of use.
  rename(`Likes` = word) # %>%
  # We focus only on the likes in this data frame
  # select(-Wishes)

# The same is done to create a data frame for the "wishes" only
evaluation_wishes_filtered <- evaluation_likes_and_wishes %>% # nolint
  unnest_tokens(word, Wishes, token = "ngrams", n = 1) %>%
  anti_join(stop_words, by = c("word")) %>%
  distinct() %>%
  filter(!word %in% undesirable_words) %>%
  filter(nchar(word) > 3) %>%
  rename(`Wishes` = word) # %>%
  # select(-Likes)

# The same is done to create a data frame for the "topics" only
evaluation_topics_filtered <- evaluation_likes_and_wishes %>% # nolint
  unnest_tokens(word, Topics, token = "ngrams", n = 1) %>%
  anti_join(stop_words, by = c("word")) %>%
  distinct() %>%
  filter(!word %in% undesirable_words) %>%
  filter(nchar(word) > 3) %>%
  rename(`Topics` = word) # %>%
  # select(-Likes)


# Correct Spelling
correct_spelling <- function(x) {
  sapply(1:length(x),
    function(y) {
      bad <- hunspell(x[y])[[1]]
      good <-
        unlist(lapply(hunspell_suggest(bad),
                      `[[`, 1))

      if (length(bad)) {
        for (i in 1:length(bad)){
          x[y] <<- gsub(bad[i], good[i], x[y])
        }
      }
    }
  )
  x
}

# Likes
corrected_spelling <-
  evaluation_likes_filtered$`Likes` %>%
  correct_spelling()

evaluation_likes_filtered$`Likes` <- corrected_spelling

# The repeated pre-processing includes:
# 1. Expanding Contractions
evaluation_likes_filtered$`Likes` <- sapply(evaluation_likes_filtered$`Likes`, expand_contractions)

# 2. Remove special Characters
evaluation_likes_filtered$`Likes` <- sapply(evaluation_likes_filtered$`Likes`, remove_special_characters)

# 3. Convert to Lower-Case for a standard form
evaluation_likes_filtered$`Likes` <- sapply(evaluation_likes_filtered$`Likes`, tolower)

# 4. Tokenization, stopword removal, short word removal, and censorship
evaluation_likes_filtered <- evaluation_likes_filtered %>% # nolint
  unnest_tokens(word, `Likes`, token = "ngrams", n = 1) %>%
  anti_join(stop_words, by = c("word")) %>%
  distinct() %>%
  filter(!word %in% undesirable_words) %>%
  filter(nchar(word) > 3) %>%
  rename(`Likes` = word)

# Wishes
corrected_spelling <-
  evaluation_wishes_filtered$`Wishes` %>%
  correct_spelling()

evaluation_wishes_filtered$`Wishes` <- corrected_spelling

### Repeat the pre-processing for the correctly spelt words ----
# This is done for the sake of the words which were split into more than one
# word after correcting the spelling mistake.

# The repeated pre-processing includes:
# 1. Expanding Contractions
evaluation_wishes_filtered$`Wishes` <- sapply(evaluation_wishes_filtered$`Wishes`, expand_contractions) # nolint
# 2. Remove special Characters
evaluation_wishes_filtered$`Wishes` <- sapply(evaluation_wishes_filtered$`Wishes`, remove_special_characters) # nolint
# 3. Convert to Lower-Case for a standard form
evaluation_wishes_filtered$`Wishes` <- sapply(evaluation_wishes_filtered$`Wishes`, tolower) # nolint

# 4. Tokenization, stopword removal, short word removal, and censorship
evaluation_wishes_filtered <- evaluation_wishes_filtered %>% # nolint
  unnest_tokens(word, `Wishes`, token = "ngrams", n = 1) %>%
  anti_join(stop_words, by = c("word")) %>%
  distinct() %>%
  filter(!word %in% undesirable_words) %>%
  filter(nchar(word) > 3) %>%
  rename(`Wishes` = word)

# Wishes
corrected_spelling <-
  evaluation_wishes_filtered$`Wishes` %>%
  correct_spelling()

evaluation_wishes_filtered$`Wishes` <- corrected_spelling

# Topics
# corrected_spelling <-
  # evaluation_topics_filtered$`Topics` %>%
  # correct_spelling()

# evaluation_topics_filtered$Topics <- corrected_spelling

### ***** Repeat the pre-processing for the correctly spelt words ----
# The repeated pre-processing includes:
# 1. Expanding Contractions
evaluation_topics_filtered$`Topics` <- sapply(evaluation_topics_filtered$`Topics`, expand_contractions) # nolint
# 2. Remove special Characters
evaluation_topics_filtered$`Topics` <- sapply(evaluation_topics_filtered$`Topics`, remove_special_characters) # nolint
# 3. Convert to Lower-Case for a standard form
evaluation_topics_filtered$`Topics` <- sapply(evaluation_topics_filtered$`Topics`, tolower) # nolint

# 4. Tokenization, stopword removal, short word removal, and censorship
evaluation_topics_filtered <- evaluation_topics_filtered %>% # nolint
  unnest_tokens(word, `Topics`, token = "ngrams", n = 1) %>%
  anti_join(stop_words, by = c("word")) %>%
  distinct() %>%
  filter(!word %in% undesirable_words) %>%
  filter(nchar(word) > 3) %>%
  rename(`Topics` = word)

### We can now perform lemmatization on the correctly spelt words ----
# We need to first create a lemma lookup table. The lemmatize_strings()
# function will then use this lookup table to replace the words.

# Think of the lemma lookup table as a subset of an entire lemma dictionary.
# This makes it easier to search for a word in the smaller lookup table
# instead of searching for a word in the entire lemma dictionary.

# Lemma lookup tables specific to a project can be made by referring to
# a pre-existing lemma dictionary. The code below shows how the "Hunspell"
# lemma dictionary is used to create  the lemma lookup table (subset of
# the dictionary).

# Lemma dictionaries include:
#   1. Hunspell: https://hunspell.github.io/ or
#                https://cran.r-project.org/package=hunspell
#   2. koRpus: https://reaktanz.de/?c=hacking&s=koRpus or
#              https://cran.r-project.org/package=koRpus
#   3. Michal Mchura (2016): https://www.lexiconista.com/
#   etc.

lemma_dictionary_for_likes <-
  make_lemma_dictionary(evaluation_likes_filtered$`Likes`,
                        engine = "hunspell")

evaluation_likes_filtered$`Likes` <-
  evaluation_likes_filtered$`Likes` %>%
  lemmatize_strings(dictionary = lemma_dictionary_for_likes)

lemma_dictionary_for_wishes <-
  make_lemma_dictionary(evaluation_wishes_filtered$`Wishes`,
                        engine = "hunspell")

evaluation_wishes_filtered$`Wishes` <-
  evaluation_wishes_filtered$`Wishes` %>%
  lemmatize_strings(dictionary = lemma_dictionary_for_wishes)

lemma_dictionary_for_topics <-
  make_lemma_dictionary(evaluation_topics_filtered$Topics,
                        engine = "hunspell")

evaluation_topics_filtered$Topics <-
  evaluation_topics_filtered$Topics %>%
  lemmatize_strings(dictionary = lemma_dictionary_for_wishes)
```

## Sentiment Analysis (Lexicon-Based)

```{r SentimentAnalysisWithNRC, include=FALSE}
nrc <- get_sentiments("nrc")

# Inner Join the Likes/Wishes with the Corresponding Sentiment(s) ----
evaluation_likes_filtered_nrc <- evaluation_likes_filtered %>%
  inner_join(get_sentiments("nrc"),
             by = join_by(`Likes` == word),
             relationship = "many-to-many")

evaluation_wishes_filtered_nrc <- evaluation_wishes_filtered %>%
  inner_join(get_sentiments("nrc"),
             by = join_by(`Wishes` == word),
             relationship = "many-to-many")

```

The "likes" refer to the answer to the question, "Write two things you liked about the teaching and learning in this course." The sentiments expressed through the "likes" are:

```{r OverallSentimentForLikes, echo=FALSE, fig.height=5, fig.width=15, message=FALSE, warning=FALSE}
# STEP 6. Overall Sentiment ----
## Evaluation Likes ----
nrc_likes_plot <- evaluation_likes_filtered_nrc %>%
  group_by(sentiment) %>%
  # You can filter by the class group if you wish
  # filter(`Class Group` == "A") %>%
  summarise(word_count = n()) %>%
  ungroup() %>%
  mutate(sentiment = reorder(sentiment, word_count)) %>%
  # `fill = -word_count` is used to make the larger bars darker
  ggplot(aes(sentiment, word_count, fill = -word_count)) +
  geom_col() +
  guides(fill = FALSE) + # Turn off the legend
  blue_grey_theme() +
  labs(x = "Sentiment", y = "Word Count") +
  # scale_y_continuous(limits = c(0, 15000)) + #Hard code the axis limit
  ggtitle("Lexicon-Based Sentiment Analysis of Course Evaluation Likes") +
  coord_flip()
plot(nrc_likes_plot)
```

The "wishes" refer to the answer to the question, "Write at least one recommendation to improve the teaching and learning in this course (for future classes)". The sentiments expressed through the "wishes" are:

```{r OverallSentimentForWishes, echo=FALSE, fig.height=5, fig.width=15, message=FALSE, warning=FALSE}
## Evaluation Wishes ----
nrc_wishes_plot <- evaluation_wishes_filtered_nrc %>%
  group_by(sentiment) %>%
  # You can filter by the class group if you wish
  # filter(`Class Group` == "A") %>%
  summarise(word_count = n()) %>%
  ungroup() %>%
  mutate(sentiment = reorder(sentiment, word_count)) %>%
  # fill = -word_count is used to make the larger bars darker
  ggplot(aes(sentiment, word_count, fill = -word_count)) +
  geom_col() +
  guides(fill = FALSE) + # Turn off the legend
  blue_grey_theme() +
  labs(x = "Sentiment", y = "Word Count") +
  # scale_y_continuous(limits = c(0, 15000)) + #Hard code the axis limit
  ggtitle("Lexicon-Based Sentiment Analysis of Course Evaluation Wishes") +
  coord_flip()
plot(nrc_wishes_plot)
```

\newpage

Chord Diagram of Likes per Class Group:

```{r ChordDiagramLikesPerGroup, echo=FALSE, message=FALSE, warning=FALSE}
nrc_likes_chord <-  evaluation_likes_filtered_nrc %>%
  count(sentiment, `Class Group`) %>%
  group_by(`Class Group`, sentiment) %>%
  summarise(sentiment_sum = sum(n)) %>%
  filter(sentiment_sum > 5) %>%
  mutate(sentiment = reorder(sentiment, sentiment_sum)) %>%
  ungroup()

circos.clear()
# Set the gap size
circos.par(gap.after = c(rep(5, length(unique(nrc_likes_chord[[1]])) - 1), 15,
                         rep(5, length(unique(nrc_likes_chord[[2]])) - 1), 15))


chordDiagram(nrc_likes_chord, transparency = .2)
title("Lexicon-Based Sentiment Analysis of Course Evaluation Likes per Class Group")
```

\newpage

Chord Diagram of Likes per Class Gender:

```{r ChordDiagramLikesPerGender, echo=FALSE, message=FALSE, warning=FALSE}
nrc_likes_chord <-  evaluation_likes_filtered_nrc %>%
  count(sentiment, `Gender`) %>%
  group_by(`Gender`, sentiment) %>%
  summarise(sentiment_sum = sum(n)) %>%
  filter(sentiment_sum > 5) %>%
  mutate(sentiment = reorder(sentiment, sentiment_sum)) %>%
  ungroup()

circos.clear()
# Set the gap size
circos.par(gap.after = c(rep(5, length(unique(nrc_likes_chord[[1]])) - 1), 15,
                         rep(5, length(unique(nrc_likes_chord[[2]])) - 1), 15))


chordDiagram(nrc_likes_chord, transparency = .2)
title("Lexicon-Based Sentiment Analysis of Course Evaluation Likes per Gender")
```

\newpage

Chord Diagram of Wishes per Class Group:

```{r ChordDiagramPerGroup_Wishes, echo=FALSE, message=FALSE, warning=FALSE}
nrc_wishes_chord <-  evaluation_wishes_filtered_nrc %>%
  count(sentiment, `Class Group`) %>%
  group_by(`Class Group`, sentiment) %>%
  summarise(sentiment_sum = sum(n)) %>%
  filter(sentiment_sum > 3) %>%
  mutate(sentiment = reorder(sentiment, sentiment_sum)) %>%
  ungroup()

circos.clear()
# Set the gap size
circos.par(gap.after = c(rep(5, length(unique(nrc_wishes_chord[[1]])) - 1), 15,
                         rep(5, length(unique(nrc_wishes_chord[[2]])) - 1), 15))

chordDiagram(nrc_wishes_chord, transparency = .2)
title("Lexicon-Based Sentiment Analysis of Course Evaluation Wishes per Class Group")

```

\newpage

Chord Diagram of Wishes per Gender:

```{r ChordDiagramPerGender_Wishes, echo=FALSE, message=FALSE, warning=FALSE}
nrc_wishes_chord <-  evaluation_wishes_filtered_nrc %>%
  count(sentiment, `Gender`) %>%
  group_by(`Gender`, sentiment) %>%
  summarise(sentiment_sum = sum(n)) %>%
  filter(sentiment_sum > 3) %>%
  mutate(sentiment = reorder(sentiment, sentiment_sum)) %>%
  ungroup()

circos.clear()
# Set the gap size
circos.par(gap.after = c(rep(5, length(unique(nrc_wishes_chord[[1]])) - 1), 15,
                         rep(5, length(unique(nrc_wishes_chord[[2]])) - 1), 15))

chordDiagram(nrc_wishes_chord, transparency = .2)
title("Lexicon-Based Sentiment Analysis of Course Evaluation Wishes per Gender")
```

\newpage

## Topic Modelling (Latent Dirichlet Allocation (LDA) based)

The goal of topic modelling is to identify latent (hidden) terms (topics) in the students' course evaluation textual feedback. In this case, a topic is a mixture of words and a student's textual feedback is a combination of one or more topics (mixed-membership model).

```{r Create_a_DTM, message=TRUE, warning=TRUE, include=FALSE}
# LDA requires the data to be presented in a Document-Term Matrix (DTM)
# format. The conversion into a DTM is done below: 
evaluation_likes_filtered_dtm <-    evaluation_likes_filtered %>%   count(`Class Group`, Likes, sort = TRUE) %>%   ungroup() %>%   cast_dtm(`Class Group`, Likes, n)
# inspect(evaluation_likes_filtered_dtm)

evaluation_wishes_filtered_dtm <-    evaluation_wishes_filtered %>%   count(`Class Group`, Wishes, sort = TRUE) %>%   ungroup() %>%   cast_dtm(`Class Group`, Wishes, n)
# inspect(evaluation_likes_filtered_dtm)

evaluation_topics_filtered_dtm <-    evaluation_topics_filtered %>%   count(`Class Group`, Topics, sort = TRUE) %>%   ungroup() %>%   cast_dtm(`Class Group`, Topics, n)
# inspect(evaluation_topics_filtered_dtm)

# Check for rows with at least one non-zero entry
rows_with_nonzero <- apply(evaluation_topics_filtered_dtm, 1, function(row) any(row != 0))

# Select rows with at least one non-zero entry
evaluation_topics_filtered_dtm_non_zero <- evaluation_topics_filtered_dtm[rows_with_nonzero, , drop = FALSE]
```

```{r train_LDA_model_for_topic_modelling, message=TRUE, warning=TRUE, include=FALSE}
likes_topic_model <- LDA(evaluation_likes_filtered_dtm,
                         k = 3,
                         control = list(seed = 7))

wishes_topic_model <- LDA(evaluation_wishes_filtered_dtm,
                          k = 4,
                          control = list(seed = 7))

topics_topic_model <- LDA(evaluation_topics_filtered_dtm_non_zero,
                          k = 3,
                          control = list(seed = 7))
```

The 2 topics for the "likes" (as guided by the LDA model) are:

1.  Topic 1: Well-Explained Lectures

2.  Topic 2: Collaborative Environment

3.  Topic 3: Well-Taught for Ease of Understanding

```{r visualizations_for_likes_topic_modelling, echo=FALSE}
likes_topics <- tidy(likes_topic_model, matrix = "beta")
likes_top_terms <-
  likes_topics %>%
  group_by (topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

likes_top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +   geom_col(show.legend = FALSE) +   facet_wrap(~topic, scales = "free") +   theme_minimal() +   theme(plot.title =            element_text(hjust = 0.5, size = 18)) +   labs(     title = "Topic Model of Course Evaluation Likes",     caption = "Top Terms by Topic (betas)"     ) +   ylab("") +   xlab("") +   coord_flip()
```

\newpage

The 5 topics for the "wishes" (as guided by the LDA model) are:

1.  Topic 1: Reduce the Workload

2.  Topic 2: Reduce the Complexity of the Labs

3.  Topic 3: Application of Data Engineering

4.  Topic 4: Application of Python

```{r visualizations_for_wishes_topic_modelling, echo=FALSE}
wishes_topics <- tidy(wishes_topic_model, matrix = "beta")
wishes_top_terms <-
  wishes_topics %>%
  group_by (topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

wishes_top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +   facet_wrap(~topic, scales = "free") +   theme_minimal() + theme(plot.title = element_text(hjust = 0.5, size = 18)) +   labs(     title = "Topic Model of Course Evaluation Wishes",     caption = "Top Terms by Topic (betas)"     ) +   ylab("") +   xlab("") +   coord_flip()
```

\newpage

The 3 topics for the recommended BI content (as guided by the LDA model) are:

1.  Topic 1: Python

2.  Topic 2: Tableau

3.  Topic 3: PowerBI

```{r visualizations_for_recommended_topics_topic_modelling, echo=FALSE}
recommended_topics <- tidy(topics_topic_model, matrix = "beta")
recommended_topics_top_terms <-
  recommended_topics %>%
  group_by (topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

recommended_topics_top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +   geom_col(show.legend = FALSE) +   facet_wrap(~topic, scales = "free") +   theme_minimal() +   theme(plot.title =            element_text(hjust = 0.5, size = 18)) +   labs(     title = "Topic Model of Recommended BI Topics",     caption = "Top Terms by Topic (betas)"     ) +   ylab("") +   xlab("") +   coord_flip()
```

\newpage

# Appendices

## Appendix A: Full Name of Variables

The following variables have been renamed to fit the correlation plots:

-   \`A. Enjoying Subject\` = \`Q02_General Questions-\>A - 1. I enjoyed the subject\`,

-   \`B. Classes Start-End\` = \`Q02_General Questions-\>A - 2. Classes started and ended on time\`,

-   \`C. Learning Environment\` = \`Q02_General Questions-\>A - 3. The learning environment was participative, involved learning by doing and was group-based\`,

-   \`D. Content Delivery\` = \`Q02_General Questions-\>A - 4. The subject content was delivered according to the course outline and met my expectations\`,

-   \`E. Clear Topics\` = \`Q02_General Questions-\>A - 5. The topics were clear and logically developed\`,

-   \`F. Oral and Writing\` = \`Q02_General Questions-\>A - 6. I developed my oral and writing skills\`,

-   \`G. Critical Thinking\` = \`Q02_General Questions-\>A - 7. I developed my reflective and critical reasoning skills\`,

-   \`H. Assessment Methods\` = \`Q02_General Questions-\>A - 8. The assessment methods assisted me to learn\`,

-   \`I. Relevant Feedback\` = \`Q02_General Questions-\>A - 9. I received relevant feedback\`,

-   \`J. Read Recommendations\` = \`Q02_General Questions-\>A - 10. I read the recommended readings and notes\`,

-   \`L. eLearning Material\` = \`Q02_General Questions-\>A - 11. I used the eLearning material posted\`,

-   \`Understood BI1 Concept 1\` = \`Q03_Level of Learning Achieved-\>B - 1. - BI1 - Concept 1 of 4: Ensemble Methods for Predictive Analytics\`,

-   \`Understood BI1 Concept 2\` = \`Q03_Level of Learning Achieved-\>B - 2. - BI1 - Concept 2 of 4: Linear Algorithms for Predictive Analytics\`,

-   \`Understood BI1 Concept 3\` = \`Q03_Level of Learning Achieved-\>B - 3. - BI1 - Concept 3 of 4: Non-Linear Algorithms for Predictive Analytics\`,

-   \`Understood BI1 Concept 4\` = \`Q03_Level of Learning Achieved-\>B - 4. - BI1 - Concept 4 of 4: Dashboarding for Business-Facing and Customer-Facing Analytics\`,

-   \`Understood BI2 Concept 1\` = \`Q03_Level of Learning Achieved-\>B - 1. - BI2 - Concept 1 of 4: Ensemble Methods for Predictive Analytics\`,

-   \`Understood BI2 Concept 2\` = \`Q03_Level of Learning Achieved-\>B - 2. - BI2 - Concept 2 of 4: Predictive Modelling Using R\`,

-   \`Understood BI2 Concept 3\` = \`Q03_Level of Learning Achieved-\>B - 3. - BI2 - Concept 3 of 4: Data Warehousing and BI Strategy Implementation\`,

-   \`Understood BI2 Concept 4\` = \`Q03_Level of Learning Achieved-\>B - 4. - BI2 - Concept 4 of 4: Data Engineering\`,

-   \`Acquired Skill 1\` = \`Q04_Competency for Technologies-\>D - 1. ChartJS\`,

-   \`Acquired Skill 2\` = \`Q04_Competency for Technologies-\>D - 2. R (includes R markdown and R plumber)\`,

-   \`Acquired Skill 3\` = \`Q04_Competency for Technologies-\>D - 3. MySQL\`,

-   \`Acquired Skill 4\` = \`Q04_Competency for Technologies-\>D - 4. Kafka\`,

-   \`Acquired Skill 5\` = \`Q04_Competency for Technologies-\>D - 5. ksqlDB\`,

-   \`Acquired Skill 6\` = \`Q04_Competency for Technologies-\>D - 6. ClickHouse\`,

-   \`Acquired Skill 7\` = \`Q04_Competency for Technologies-\>D - 7. Linear and Non-Linear ML Algorithms in the caret package\`,

-   \`Group Project\` = \`Q05_Quality of Teaching Strategies-\>E - 1. Group project\`,

-   \`Labs Manuals\` = \`Q05_Quality of Teaching Strategies-\>E - 2. Lab manuals that outline the steps to follow during the labs\`,

-   \`Lab Submissions\` = \`Q05_Quality of Teaching Strategies-\>E - 3. Required lab work submissions at the end of each lab manual that outline the activity to be done on your own\`,

-   \`Supplementary Videos/Audio\` = \`Q05_Quality of Teaching Strategies-\>E - 4. Supplementary videos/audio to watch/listen to\`,

-   \`Lecture Slides\` = \`Q05_Quality of Teaching Strategies-\>E - 5. Lectures slides\`,

-   \`Lecture Notes\` = \`Q05_Quality of Teaching Strategies-\>E - 6. Lecture notes on some of the lecture slides\`,

-   \`Quality of Lectures\` = \`Q05_Quality of Teaching Strategies-\>E - 7. The quality of the lectures given (quality measured by the breadth (the full span of knowledge of a subject) and depth (the extent to which specific topics are focused upon, amplified, and explored) of learning - NOT quality measured by how fun/comical the lectures are)\`,

-   \`Online for Theory\` = \`Q05_Quality of Teaching Strategies-\>E - 8. The division of theory and practice such that most of the theory is done during the recorded online classes and most of the practice is done during the physical classes\`,

-   \`Recording of Online\` = \`Q05_Quality of Teaching Strategies-\>E - 9. The recordings of online classes\`

\newpage

## Appendix B: Raw Qualitative Data

### Likes

The raw data of the likes is as follows:

```{r RawLikesData, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(course_evaluation_dataset$`Q07_Likes->G - 1. Write two things you liked about the teaching and learning in this course.`, caption = "Write two things you like about the teaching and learning in this unit so far", digits = 4, col.names = "Comment (Likes)", align = "l", escape = TRUE, longtable = TRUE, booktabs = TRUE, linesep = "\\hline") %>%
  column_spec(1, width = "35em", extra_css = "border-bottom: 1px solid;") %>% 
  kable_styling(latex_options="scale_down")

# course_evaluation_dataset$`Q07_Likes->G - 1. Write two things you liked about the teaching and learning in this course.` %>%
  # my_kable_styling("Write two things you like about the teaching and learning in this unit so far")
```

\newpage

### Wishes

The raw data of the wishes is as follows:

```{r RawWishesData, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(course_evaluation_dataset$`Q07_Wishes->G - 2. Write at least one recommendation to improve the teaching and learning in this course (for future classes)`, caption = "Write at least one recommendation to improve the teaching and learning in this unit (for the remaining weeks in the semester)", digits = 4, col.names = "Comment (Wishes)", align = "l", escape = TRUE, longtable = TRUE, booktabs = TRUE, linesep = "\\hline") %>%
  column_spec(1, width = "35em", extra_css = "border-bottom: 1px solid;") %>% 
  kable_styling(latex_options="scale_down")

# course_evaluation_dataset$`Q07_Wishes->G - 2. Write at least one recommendation to improve the teaching and learning in this course (for future classes)` %>%
  # my_kable_styling("Write at least one recommendation to improve the teaching and learning in this unit (for the remaining weeks in the semester)")
```

\newpage

## Appendix C: Additional Topics to Include in the Course

The raw data of the addtional topics to include is as follows:

```{r AdditionalTopics, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(course_evaluation_dataset$`Q06_Topics to Add->F - 1. Are there any topics that you recommend should be added to in addition to the ones already in the BI1 and BI2 course outlines?`, caption = "Are there any topics that you recommend should be added to in addition to the ones already in the BI1 and BI2 course outlines?", digits = 4, col.names = "List of Topics", align = "l", escape = TRUE, longtable = TRUE, booktabs = TRUE, linesep = "\\hline") %>%
  column_spec(1, width = "35em", extra_css = "border-bottom: 1px solid;") %>% 
  kable_styling(latex_options="scale_down")
```
